### 2013-07-22 doc/asplos14/relatedwork.tex
change vocie of related work

\vspace{0.5ex}
\noindent{\bf Software distributed shared memory.} 
%\section{Software distributed shared memory} 
The goal of providing a shared memory abstraction for a distributed
memory system goes back nearly 30 years. Here I present a few of the
ideas explored in this area.

Much of the innovation in SDSM has occurred around reducing the
synchronization cost of doing updates. The first DSM systems,
including IVY~\cite{Li:1989:MCS:75104.75105}, used invalidations to
provide sequential consistency, which imposed significant
communication cost for write-heavy workloads.  Later systems supported
more relaxed consistency models, including release consistency, which
reduced the cost by allowing updates to be buffered until
synchronization occurred. Furthermore, multiple writer protocols that
sent only modified data were developed to help combat false
sharing. The
Munin~\cite{Bennett:1990:MDS:99163.99182,Carter:1991:IPM:121132.121159}
and TreadMarks~\cite{Keleher:1994:TDS:1267074.1267084} systems
exploited both of these ideas, but some coherence overhead was still
required. In contrast, Grappa's delegate-based approach to updates
avoids synchronization overhead entirely, providing sequential
consistency for data-race-free programs without the cost of a
coherence protocol. This cost of this communication is mitigated through latency
tolerance.

@@

\vspace{0.5ex}
\noindent{\bf Partitioned Global Address Space languages.} 
%\section{Partitioned Global Address Space languages} 
The high-performance computing community has largely discarded the
coherent distributed shared memory approach in favor of the
Partitioned Global Address Space (PGAS)
model. Split-C~\cite{Krishnamurthy:1993:PPS:169627.169724} is the
earliest example I know of this style of language; contemporary
examples include Chapel~\cite{Chamberlain:2007}, X10~\cite{X10:2005},
Co-array Fortran~\cite{Numrich:1998:CFP:289918.289920} and
UPC~\cite{upc:2005}. Grappa shares many parts of its design philosophy
with these languages.

@@

Grappa's latency-tolerant approach to irregular and graph applications is
catching on. Colleagues at PNNL have developed GMT~\cite{GMT}, a system that
follows the same basic approach as Grappa but with more of a focus on
node-shared resources. After discussions with the Grappa team, the next version of GraphLab will also include
lightweight context switching for latency tolerance \cite{graphlab-next}.

>>>>

\vspace{0.5ex}
\noindent{\bf Software distributed shared memory.} 
%\section{Software distributed shared memory} 
The goal of providing a shared memory abstraction for a distributed
memory system goes back nearly 30 years. Much of the innovation in SDSM has occurred around reducing the
synchronization cost of doing updates. The first DSM systems,
including IVY~\cite{Li:1989:MCS:75104.75105}, used invalidations to
provide sequential consistency, which imposed significant
communication cost for write-heavy workloads.  Later systems supported
more relaxed consistency models, including release consistency, which
reduced the cost by allowing updates to be buffered until
synchronization occurred. Furthermore, multiple writer protocols that
sent only modified data were developed to help combat false
sharing. The
Munin~\cite{Bennett:1990:MDS:99163.99182,Carter:1991:IPM:121132.121159}
and TreadMarks~\cite{Keleher:1994:TDS:1267074.1267084} systems
exploited both of these ideas, but some coherence overhead was still
required. In contrast, Grappa's delegate-based approach to updates
avoids synchronization overhead entirely, providing sequential
consistency for data-race-free programs without the cost of a
coherence protocol. This cost of this communication is mitigated through latency
tolerance.

@@

\vspace{0.5ex}
\noindent{\bf Partitioned Global Address Space languages.} 
%\section{Partitioned Global Address Space languages} 
The high-performance computing community has largely discarded the
coherent distributed shared memory approach in favor of the
Partitioned Global Address Space (PGAS)
model. Example include Split-C~\cite{Krishnamurthy:1993:PPS:169627.169724},
Chapel~\cite{Chamberlain:2007}, X10~\cite{X10:2005},
Co-array Fortran~\cite{Numrich:1998:CFP:289918.289920} and
UPC~\cite{upc:2005}. Grappa shares many parts of its design philosophy
with these languages.

@@
